### 2023-02-15 README.Rmd
Clean README a little [no ci]

```bash
cd ~/rocker_test
sudo docker build -t rang .
sudo docker run --rm --name "rangtest" -ti rang
```

@@

One can also cache (or archive) the R packages from CRAN at the time `dockerize` is executed. The cached R packages will then transfer to the container. Please note that system requirements (i.e. `deb` packages) are not cached.

@@

```bash
cd ~/rocker_test
sudo docker build -t rang .
sudo docker run -p 8787:8787 -e PASSWORD=abc123 --rm --name "rangtest" -ti rang
```

>>>>

```bash
cd ~/rocker_test
docker build -t rang .
docker run --rm --name "rangtest" -ti rang
```

@@

One can also cache (or archive) the R packages from CRAN and Github at the time `dockerize` is executed. The cached R packages will then transfer to the container. Please note that system requirements (i.e. `deb` packages) are not cached.

@@

```bash
cd ~/rocker_test
docker build -t rang .
docker run -p 8787:8787 -e PASSWORD=abc123 --rm --name "rangtest" -ti rang
```
